Dataset table

### 2018-02-07 analyses/04-table-datasets.Rmd
Typos

## Age ranges
age_ranges <- lapply(trees, function(tree) rev(range(tree.age(tree)$age)))
age_ranges <- unlist(lapply(age_ranges, function(age) paste(age, collapse = " - ")))

@@

## Table caption
table_caption <- "Details of the datasets used in this study. Note that although Brusatte2014 and Bapst2016 cross the Cretaceous Palaeogene (K-Pg) mass extinction there are not enough taxa post K-Pg to investigate the effects of the mass extinction on disparity."

>>>>

## Age ranges
age_ranges <- lapply(trees, function(tree) rev(range(tree.age(tree)$age)))
age_ranges <- unlist(lapply(age_ranges, function(age) paste(age, collapse = " - ")))
## Note that I've had to correct these for Bapst2016 (207.2) and Brusatte2014 (168.5) due to 
## the rerooting that occurred when removing taxa

@@

## Table caption
table_caption <- "Details of the datasets used in this study. Age ranges are root time to most recent tip taxon."
